Title?

### 2019-08-21 April/paper_recovered.tex
On hold.

\begin{abstract}

%Verizon and At\&T, two major Internet service providers (ISPs), are offering
%shared data plans, where multiple users may purchase and share a single pool of
%data. 
We investigate data-exchange platforms for wireless users. The
2cm (2nd exchange market) creates a secondary market where users can buy and sell data from each other.
The ISP owns and moderates 2cm, which prevents the secondary market from
acting as a competitor, and provides the ISP with free market research.
Competition is desired, as it provides incentive for the ISP to protect
and care for its end users.
In this work, we design a strategy space, and a distributed Progressive Second Price (PSP) mechanism
that extends individual privacy to the global space, allowing a secondary market to compete with its parent ISP. 
The PSP auction has a single degree of freedom, the reserve price. We suggest
that data exchange markets allow for greater flexibility in mechanism
design due to the connectedness of the wireless network, and the fact that data
exchange is a pure ``point of sale" market.
We propose additional degrees of freedom, and derive modifiers
to represent the deformation of the strategy space. 
Using a game theoretic analysis, we derive a new strategic
framework, removing restrictions that are dependent only on bandwidth. We
model user valuation as a strategic response to market dynamics, and propose
the resulting self-contained, self-balancing pricing system. 
We examine mutations in market dynamics resulting from the new modifiers, and
using set theory, we prove that the symmetry of our strategy space provides built-in
conditions for convergence, and upholds the properties of truthfulness, efficiency and
incentive compatibility, arriving at a Nash equlibirium.
\end{abstract}

\iffalse
We further provide bounds on the auction duration, 
with respect to the classic throughput problem.
and provide simulated results on convergence time to support our (FIND
COMPETITVE RATIO!), and a bound
on the convergence of our mechanism. We extend the works of cite!cite!
i.e. (market influence/EQ,social EQ,payment/allocation models) OR (bandwidth, data bundles, distributed
market algorithms) and show the existence of a dynamic global market equilibrium, allowing for a unique set of market dynamics.
\fi

@@

In this work, we propose a PSP auction mechanism for a secondary data
market's valuations to be hidden from its parent ISP.
A quality of the PSP auction is that
demand information is not known centrally, rather, it is distributed in the
buyers' valuations. The mechanism for an auction is defined
as \emph{distributed} when the allocations at any element depend only on
\emph{local} state, no single entity holds a global market knowledge. We consider the multi-auction, where there are many auctioneers, each holding
thier own local auction. The auction mechanism may be described as
pure-strategy progressive game with incomplete, but perfect information.

In a PSP mechanism, bids consist of (1) a quantity and
(2) a unit-price. Buyers submit bids until an
($\epsilon$-Nash) equilibrium is reached.

In the distributed setting, we assume users have a binary type, either seller,
i.e. auctioneer, or buyer, and so user strategy changes according to the user
type.

We use game theory to show that the PSP mechanism, when applied to a
pure ``point-of-sale" market, results in a primary
$\epsilon$-Nash market equilibrium that is the dominant strategy in the
multi-auction system.
To the best of our knowledge, this is the first work to provide a comprehensive
derivation of a truthful mechanism that is self-contained within a dynamic market
topology. The market
topology and the user strategy are organically determined by the impact of user
behavior on market dynamics, and so determines a minimally optimal objective
representing user valuation globally, and so fufills an additional property of
economy over time and space. We further model the ISP as a deaf and blind
user, who nonetheless holds the power to create a monopoly, thereby providing a free
market space in which the market may operate, and real-world implications.

The market strategy is based on providing users with an incentive framework, and
so rational users choose a collaborative exchage. 
%\textbf{Remark:} It is certainly possible to extend the mechanism, alleviating the
%restrictions introduced by the CMHK secondary market. We reserve this for
%future work.
In classic mechanism design, with multiple user types, there is no single
way to design the transformation from the direct revelation mechanism to its
corresponding computational design. We apply a modifier to the PSP mechanism in
order to mutate the strategy space, following dynamic user
correspendence. As in \cite{lazar}, we take the direct
approach by guessing the right modifier, and context, such that we have the
desired result by composition with the PSP rules. 
As in \cite{lazar}, the incentive for a
user to truthfully reveal its type is built into the user strategies. Then,
local equilibria follow as a result of incentive
compatibility characterizing best strategy moves. \\ 
\textbf{Remark:} The terms ``bid" and ``strategy" are often interchangable,
from mechanism design and game theory, respectively.\\
\iffalse
We claim that our formulation not only holds the desired VCG qualities,
but minimizes comminication overhead 
and auction duration, resulting in a convergence time (FIND COMPETITIVE RATIO?)
with respect to the classic throughput problem. 
\fi

The user strategies are organic in that they are natural, or
induced by the dynamic market itself. In other words, adhering to the second-price rule,
where price is derived from autonomous demand, we have a strategic
progressive auction, and a multi-objective equilibria.
This is the (built-in) transformation from the
direct-revelation mechanism to the desired message space, (OWN WORDS) where each user
message defines a strategic point, which we may interpret as a move to a better
market position. Then, in the limit of the data-model, a user reveals its
valuation of a quantitiy of data-resource over the whole range of possible demands.

The secondary market applies the PSP auction rules over a wireless network. The
wireless users' data incentives create a pure ``point-of-sale" market. We prove
that there exists a primary $\epsilon$-Nash market equilibrium that is
the dominant strategy in the multi-auction system.
To the best of our knowledge, this is the first work to provide a comprehensive
derivation of a truthful mechanism that is self-contained within a dynamic market
topology. The market topology and the user strategy are organically determined by the impact of user
behavior on market dynamics. We determine a globally optimal objective, and a
strategy that satisfies the desires properties of competition, and
economy over time and space.

We address several topics under discussion in the real-monetary market of virtual
data ownership. The proliferation of services that are moving from grid-based to node-based communication
calls for algorithms designed for optimization in this space. Direct and
network-based communication between mobille devices allows for a simple
mutation of classic optimization models.

The secondary market provides a unique opportunity for social equilibrium, as it
allows users to share data without sharing the same data plan, a restriction in
most ISPs, such as \cite{att}. We reason that a secondary market
approximates local, free-market economy. Laws such as \cite{fedbill} exist to regulate ISPs
as they have historically come close to monopolizing regional markets, leading
to consumer abuse. Our mechanism
takes advantage of the opportunity for full generalization provided by CMHK.
Our secondary market is adapted from the idea behind 2cm, the goal of allowing
users to buy and sell data. We claim that it is simple
to adapt our mechanism to the data share
plans published by any major ISP, for example AT\&T's data share plan \cite{att}.
We argue that data-sharing plans in general may be
biased against the end-user. Adding devices to a shared-data plan includes a
base fee for other services that have relatively small demand in comparison to
the demand for data. Effectively, users must pay for services that go unused in
order to increase the amount of data for a shared plan. Flexible data-sharing
plans are similar to the CMHK market, where a limited number of devices may
share a single data plan. A shared-data plan, however limited, offers better economy
by creating primary users with a service package with a lot of data, and
limited number of secondary users that are only using data \cite{att}.
The CMHK model allows for primary and secondary users to freely correspond,
without the restriction of a static primary-secondary user association.
This effectively creates a competitive secondary market, and contributes to the
dynamics of a free-market economy. Market competition is a desirable quality in
free markets, and is encouraged, particularly in wireless and data services. In
fact, California Legistature has recently passed laws promoting
competition and enforcing fair practice of ISPs \cite{cabill}.
The paper is organized as follows... (TODO)

Progressive second price auctions (PSPs) were proposed
in \cite{lazar}, \cite{diffserve} to provide a dynamic network service pricing
scheme to provide consistent services for network bandwith users.
\cite{diffserve} conducts a game theoretic analysis, deriving
optimal strategies for buyers and brokers, and further shows the existence
of networkwide market equilibria based on their game-theoretic
model. Constructing necessary and sufficient conditions for the stability
of the game allows the sustainability of any set
of service level agreement configurations between Internet service
providers.
It was shown, in \cite{lazar}, that the mechanism may converge to a Nash market
equilibria for differentiated services
allocated between multiple agents when all players bid their real marginal valuation
of the bandwidth resource. In other words, the PSP constraints are
sufficient to attain the desirable property of truthfullness through incentive
compatibility. The pricing mechanism upholds the \emph{exclusion-compensation
principle}, user $i$
pays for its allocation so as to exactly cover the ``social opportunity cost"
which is given by the declared willingness to pay (bids) of the users who are
excluded by $i$'s presence, and thus also compensates the seller for the maximum lost potential
revenue \cite{lazar}.

In \cite{zheng}, the ISP matches buyers and
sellers to each other, and determines the amount
of data that users can buy or sell. A buyer always pays her
bid price for any data bought, and similarly a seller always
receives his bid price, with any differences between the amounts
paid and received acts as revenue for the ISP.
%Then, the ISP will match buyers and sellers so as to optimize its revenue.

Most previously studied data auctions aim to mitigate net-
work congestion. For example, \cite{pubacs} considers a scheme in
which users place bids on each transmitted data packet and the
ISP admits packets in order of decreasing bids.

%\iffalse
\section{Distributed Progressive Second Price Auctions}

@@

% MECHANISM
\subsubsection{The PSP Mechanism}\label{mechanism}
The PSP auction as given in \cite{lazar} and \cite{semret} is designed for the
problem of network bandwidth allocation, and is analyzed as a noncooperative
game where $i\in\mcI$ agents buy the
fixed amount of bandwidth $d_i^j$ from sellers $j\in\mcI$.
The market price function (MPF) for a buyer-seller pair is,
% MARKET PRICE
\begin{align}\label{dataprice}
\begin{split}
    P_i^j(z, s_{-i})= \inf\bigg\lbrace y\ge 0 : D_i^j(y, s_{-i}) \ge z \bigg\rbrace,\\
\end{split}
\end{align}
and is the of minimum prices a user bids in
order to obtain bandwidth $z$ given opponent profile $s_{-i}$. 
The maximum available quantity of data in auction
$j$ at unit price $y$ given $s_{-i}^j$ is,
% INVERSE DEMAND
\begin{align}\label{datapriceinverse}
\begin{split}
    D_i^j(y, s_{-i}) &= \bigg[ D^j - \sum_{p_k^j>y,k\ne i} d_k^j  \bigg]^+,
\end{split}
\end{align}
where $D^j$ is the total amount of bandwith that user $j$ has to offer.
% DATA ALLOCATION RULE
For each $i \in \mcI$, the allocation from auction $j$ is,
% and so for profile $s_i$, for any $i \in \mcI$,
\begin{align}\label{dataallocation}
    a_i^j(s) &= \min\bigg( d_i^j, 
    D_i^j(p_i^j,s_{-i}^j)\bigg).
\end{align}
Finally, we have the cost of the allocation,
% DATA COST
\begin{align}\label{datacost}
    c_i^j(s) = \displaystyle\sum_{k\ne i} 
p_k^j \big[a_k^j(0; s_{-i}^j)
    -a_k^j(s_i^j;s_{-i}^j)\big].
\end{align}

It was shown, in \cite{lazar}, that the mechanism may converge to a Nash market
equilibria for differentiated services
allocated between multiple agents when all players bid their real marginal valuation
of the bandwidth resource. In other words, the PSP constraints are
sufficient to attain the desirable property of truthfullness through incentive
compatibility. The pricing mechanism upholds the \emph{exclusion-compensation
principle}, user $i$
pays for its allocation so as to exactly cover the ``social opportunity cost"
which is given by the declared willingness to pay (bids) of the users who are
excluded by $i$'s presence, and thus also compensates the seller for the maximum lost potential
revenue \cite{lazar}.
{
\definition{(Nash Equilibrium)}
A Nash equilibrium is defined as a strategy vector, or, in terms of PSP, a bid
profile $s$,
from which no player has a unilateral incentive to deviate (Johari, 2004)
(EXPAND?)
}\\

The PSP rules assume that an agent's valuation is represented by an elastic valuation function.
\definition{\cite{lazar}}
A real valued function, $\theta(\cdot): [0,\infty) \rightarrow [0,\infty)$, is an \emph{(elastic) valuation
function} on $[0, D]$ if 
\begin{itemize}
    \item $\theta(0) = 0$,
    \item $\theta$ is differentiable,
    \item ${\theta}' \ge 0$, and ${\theta_i}'$ is non-increasing and continuous,
     \item There exists $\gamma > 0$, such that for all $z \in [0,D]$,
${\theta}'(z) > 0$ implies that for all $\eta \in [0, z), {\theta}'(z) \le
{\theta}'(\eta)
- \gamma(z - \eta)$. 
\end{itemize}
The function $\theta'(\cdot)$ on $[0, D]$ is called an (elastic) demand
function.
In the PSP market, a
user is considered truthful if their bid price equals their marginal valuation,
i.e. $p_i^j = {\theta_i^j}'$.
%\fi

@@

We construct the model for a PSP data auction for mobile users
particpating in CMHK's secondary data-sharing market.
Define the index set $\mcI = \lbrace 1, \cdots, I\rbrace$ to represent the set of users who purchase or sell
data from other users. We again define the bidding profile for any user to be 
$s \equiv
[s_i^j] \in \mcI \times \mcI$, and $s_{-i} \equiv [s_1^j , \cdots , s_{i-1}^j , s_{i+1}^j , \cdots
, s_I^j]_{j\in\mcI}$ as the profile of user $i$'s opponents. 
Our strategy space is the vector space of all buyer $i$'s \emph{possible} bids,
$S_i=\Pi_{j\in\mcI} S_i^j$, and $S_{-i} =\Pi_{j\in\mcI} \Pi_{k\ne i\in\mcI} S_i^j$ the
set of opponent profiles. We assume that the users are connected.
A buyer submits bids directly to sellers. Users prefer to participate in the CMHK secondary market as it allows them to purchase
additional data for a cost less than the overage fee set by the ISP. We assume
that users are selfish, and therefore rational. 
Thus we assume that all users submit bids in order to maximize their
(private) valuation functions. 
In general, user preferences are defined by a utility function, $u$, which 
represents a users' valuation of an allocation minus the price.
Absent the cost or revenue from trading data, CMHK users gain utility from consuming
data. 
We assume that data is a unary resource belonging to the seller, and
therefore we identify each local auction with the identity of the seller
$j\in\mcI$.
We further show that user valuation satisfies the conditions for an
elastic demand function.
\iffalse:
\definition{(Elastic demand) \cite{lazar}}
A real valued function, $\theta(\cdot): [0,\infty) \rightarrow [0,\infty)$, is an \emph{(elastic) valuation
function} on $[0, D]$ if 
\begin{itemize}
    \item $\theta(0) = 0$,
    \item $\theta$ is differentiable,
    \item ${\theta}' \ge 0$, and ${\theta_i}'$ is non-increasing and continuous,
     \item There exists $\gamma > 0$, such that for all $z \in [0,D]$,
${\theta}'(z) > 0$ implies that for all $\eta \in [0, z), {\theta}'(z) \le
{\theta}'(\eta)
- \gamma(z - \eta)$. 
\end{itemize}
\fi
In the PSP market, a
user is considered truthful if their bid price equals their marginal valuation,
i.e. $p_i^j = {\theta_i^j}'$.
Finally, we assume in the CMHK market that a buyers' budget is always
sufficient, as the alternative is to pay the overage fee to the ISP.

@@

Consider the grid of bid proiles, $s$, representing the distributed PSP auction
mechanism in the CMHK market, each buyer $i$ will
have information from each seller $j$, as well as opponent profiles $s_{-i}$
from each auction in which it is participating, and therefore
in the extreme case, where $i$ submits bids to all auctions $j\in\mcI$, buyer
$i$ gains access to the full grid $s$. However, 
sellers can only gain information about the market grid by observing buyer
behavior in their local auction.
In our current formulation, we do not allow a seller to host multiple
auctions(FUTURE WORK?). Thus, the buyers are able to directly and globally
influence global market dynamics, with the sellers taking a secondary role
(FIND IN ANOTHER PAPER FOR SUPPORT OR OBVIOUS ENOUGH?).

\subsection{The Data Market Problem}

We determine the need for privacy in the data-sharing market. In \cite{zheng},
it is assumed that the ISP interferes in 2cm (market) dynamics, and will maximize the
gap between supply and demand in each transaction, exacting the difference as
revenue. We notice that this market behavior is suspiciously monopolistic, as a
single entity holds the global market power. It is further claimed in
\cite{zheng} that user bids are truthful as they are guaranteed to receive
their bid. We argue that this model represents an ``unwitting" buyer and an
equally uninformed seller, as they have no intution of fair market value.
Thus, in the interest of social good, we aim to provide a method to arrest
anti-competitive conduct by ISPs. Thus our motivation to adapt the PSP auction,
as it is easily distributed, and further has the property that user valuation
functions are private. We propose an alternative to the centralized data
exchange market that will prevent the exploitation of wireless users by their ISPs.

We aim to design a distributed PSP auction, and a strategic framework that
determines the bidding behavior of users in a wireless network.
The auction design must must meet a certain set of known
criteria: 1) \emph{truthfulness}, 2) \emph{individual rationality/
selfishness}, 3) \emph{social welfare maximization}. For the secondary data exchange
market, we determine that the
strategy space must meet additional criteria: 4) \emph{privacy and
independence from the ISP}, 5) \emph{locally fair division}, and vg)
\emph{minimize crossover in buyer/ seller pools}.
Thus, we propose a strategic framework to replace centralized data exchange
markets, e.g. 2cm. The framework will act as a host for our distributed PSP
mechanism, defining the strategy space and directing user correspondance.

We define an \textbf{opt-out function}, $\g_i$, associated with a buyer $i$ as
part of its type. Buyer $i$, when determining how to aquire a possible allocation $a$,
will determine its bid quanities by,
\begin{equation}\label{opt-out}
    \g_i(a) = [\g_i^j(a)]_{j\in\mcI}.
\end{equation}
In a general sense, $\g_i$ applies our user strategy to the PSP rules.

\subsubsection{Truthfulness.}
We prove that the dominant strategy for buyers is to submit coordinated bids,
where all bids the buyer submits are equal. Our motivation for coordinated bids
comes from the idea of potential games \cite{shapely}. In potential games, the
incentive of all users to change strategy can be expressed as a single global
function. We map the incentive of a buyer over all auctions $j\in\mcI$ to a
single potential function. This is a standard method that is used often, as it
simplfies the analysis of both strategy and auction design. 
We define the composition,
$$
     \g_i^j \circ a = \g_i^j(a) = \frac{a_i^j}{j},
$$
to be the buyer strategy with respect to quantity. We will prove that for each
buyer $i\in\mcI$ that $g_i^j(a)$ is equal $\forall \ j$. Finally, we prove the necessary condition of an $\epsilon$-best
reply: a new bid price must differ from the last by at least $\epsilon$.
Thus, our strategic bid is an $\epsilon$-best response.

\subsubsection{Individual rationality.}
We prove that a buyer cannot have a negative utility. Our
strategic framework creates an incentive for the seller to maintain a local
equilibrium, where supply equals demand. 
We define the reserve price for seller $j$ as,
\begin{equation}\label{newprice}
    p_*^{j} = p_{i^*}^{j} + \epsilon,
\end{equation}
where $i^*$ is the highest losing bidder with respect to bid price.
We claim that the choice of reserve price $p_*^j$ does not force any buyers out
of the local auction. 
A truthful bid implies that the new bid price differs from the last bid price by at least
$\epsilon$. As a seller must distribute bid vectors to all
buyers in its auction, we reason that the seller may employ a strategic caveat.
The seller will notify a buyer who is subject to a market shift by changing its
bid at the appropate index, and provide a proof by cases.

\subsubsection{Social welfare maximization.}
We claim that this is a natural consequence of PSP. Additionally,
the mechanism is self-contained, and as prices are derived from market dynamics, there cannot be any nefarious or
criminal entity negatively influencing the market.

In the original bandwidth-sharing model, the allocation role defines the active edges in a network for a particular bidder. 
The flexibily of correspondance, and
the ability for instantaneous communication in the distributed wireless network, allows for a more general, and
thus adaptive strategy. We therefore introduce additional restrictions on
defining properties of PSP multi-auctions, and claim they are normal.

\subsubsection{Privacy and independence from the ISP.}
 In
our model, free-market exchange is protected as privacy is integrated into the
mechanism. Our design enforces privacy by a mutation of user type, where
the ISP is represented by the blind, deaf user $\kappa$, who does not participate
in any auctions, but nonetheless holds the power to create a monopoly. At time $t=0$, a seller $j$ entering the market will have
submitted bid $s_\kappa^j =(D^j, \epsilon)$ to the public data exchange
platform, and so the initial bid $s_\kappa^j$, is public knowledge. 
The, the auction
begins at time $t>0$, and at $t=0$, $j$ will,
initializing its reserve price by holding a single bid iteration.
Sellers do not update pricing information with the ISP, thereby hiding
its local market price in the data-exchange market. As the ISP has limited
information from its ``competitor", it is unable to sabatoge prices derived
from fair market competition.
Thus, we claim that our model supports and protects the secondary market, allowing it
to be in direct competition with its parent ISP, and so contributes to the
regulation of ISPs \cite{fedbill} and supports a regional free-market economy
with respect to wireless data \cite{cabill}.
We will assume that the cost of participating in the secondary market is
absorbed by the bid fee, which could represent data used in submitting bids, or
a fee charged per unit of data, or a flat rate charged at the completion of the
purchase. We do not model ISP revenue, but assume it may be extracted from the
bid fee at $t=0$.

\subsubsection{Locally fair division.}

\subsubsection{Minimize crossover in buyer/ seller pools.}
%A mutation characterized by a new variable cost, absorbed into the bid fee,
%represents the fact that CMHK users are denied resale and carryover of shared
%data, effectively creating a form of liability with each transaction. 
We determine that the set of buyers and sellers participating
in a single equilibrium is bounded by the potential indirect costs of
participation. We will denote this individual cost to each user as
$\varrho$. The indirect cost is the portion of the bid fee
$\epsilon$ that is dependent on the underlying network and the individual.
Observing that $\varrho$ indirectly effects user utility,
and therefore acts to establish a natural budget for each user. We give this
constraint as, 
\begin{equation}\label{poolbnd}
    u \le \varrho,
\end{equation}
which may be interpreted as the effort a rational user is willing to expend
on its message space, and serves to limit the size of the buyer/seller pools. 
This information may be collected from a specific
device's configuration, i.e. enabled roaming, daily data restrictions.
It is clear that an unconstrained
market, even with a finite number of users, could suffer from the
expense of many local auctions trading an infinitely divisible resource, thus
$\varrho$ is interpreted as
the ``liability" component of $\epsilon$ attempts to regulate network congestion.

In order derive a distributed PSP implementation that arrives at an optimal
objective,
we analyze the behavior of users in a dynamical data exchange market. 
Buyers and sellers are able
to change their bid strategies asychronously and serially, using local information to determine their strategy. 
A users' local strategy space is therefore nondeterministic, and the prefererences of users
are subject to change, i.e. binary dependence.
Then, from \emph{Arrow's Theorem}, we have that no deterministic strategy can
provide a mapping of the preferences of users into a market-wide (complete
and transitive) strategy. As individual bids cannot map to a general objective, a better market
position can only be determined by an adaptive strategy.
We define a move to a better market position to be synonymous with a
strategic bid.

\section{Strategic Framework}

@@

We address the market risks and securities in our secondary data exchange market. 
We provide a game-theoretic model of a real market progression, which we use to
derive, then define, adaptive variables. 
Assuming equal bandwidth for all users, and derive a globally optimal strategy suited for
users with local information in a distrubuted data-sharing model.

Our mechanism allows a buyer
to \emph{opt-out} of auctions by submitting zero bids. This strategy maximizes
utility while minimizing the number of positive bids submitted to the overall
market. 
% OPT-OUT BUYER
We define each buyer as a user $i\in\mcI$ with quasi-linear utility
function $u_i = [u_i^j]_{j\in\mcI}$, a buyers' utility function is of the form,
\begin{equation}\label{buyerutility}
    u_i = \theta_i \circ (\g_i(a)) - c_i,
\end{equation}
where the composition of the elastic valuation function $\theta_i$ with $\g_i$
distributes a buyers' valuation of allocation $a$ across local markets (and thus
multiple sellers).
In this way we extend the PSP rules described
in \cite{semret} to design equilibria across subsets of local data-exchange markets.

>>>>

\begin{abstract}
We investigate the 2cm app, a data-exchange platform published for China Mobile Hong
Kong 4G Pro Service Plan customers. Telecommunications ISPs' revenue is typically
gained by charging users a fixed fee for a maximum amount
of data usage in a month, i.e., a monthly data cap \cite{???}. 
2cm's (2nd exchange market) data exchange platform allows users to submit
bids to buy and sell data.
This usage model, is, as far as our knowledge, the first data trading
platform that allows customers to buy and sell their own data.
We describe a distributed auction mechanism for data exchange inspired by the
classic PSP throughput problem,
and prove that our distributed data exchange mechanism provides incentive
compatibility (social choice function), and that we have efficiency
using only partial valuation information of each participant in an exchange market.

In applying a distributed PSP implementation to CMHK market, we
find that
the market is able to achieve an equilibrium as the sellers and buyers have an
incentive for a collaborative exchange, and design our mechanism tp provide the functions
for effective communication between the connected users. We claim that in
this secondary market our formulation holds the desired VCG qualities through the construction of a
probable equilibrium \cite{???}. We further provide bounds on the auction duration, 
with respect to the classic throughput problem.
and provide simulated results on convergence time to support our (FIND
COMPETITVE RATIO!), and a bound
on the convergence of our mechanism. We extend the works of cite!cite!
i.e. (market influence/EQ,social EQ,payment/allocation models) OR (bandwidth, data bundles, distributed
market algorithms) and show the existence of a dynamic global market equilibrium, allowing for a unique set of market dynamics.
\end{abstract}

@@

(NOTE: THE INTRODUCTION IS CURRENTLY A COLLECTION OF NOTES AND PARTIAL
SENTENCES)
In this work, we propose \emph{a distributed progressive second price (PSP) auction in
order to maximize social utility in the CMHK market}. Using the
distributed PSP mechanism on CMHKs data
exhange platform, we show that for cellular data allocated between multiple users there
exists an $\epsilon$-Nash market equilibria. A quality of the PSP auction is that
demand information is not known centrally, rather, it is distributed in the
buyers' valuations. The mechanism for an auction is defined
as \emph{distributed} when the allocations at any element depend only on
\emph{local} state: the quantity offered by the seller at that element, and the
bids for that element only \cite{lazar}. In this work, the proposed mechanism
allows the distribution of bids, where there are many ISPs each holding
thier own local auction; there is no entity that holds a global market knowledge.

In a PSP mechanism, bids consist of (i) an available (required) quantity and (ii) a unit-price (calculated
using its own demand functions). Buyers submit bids cyclically until an
($\epsilon$-Nash) equilibrium is reached and a local auction is concluded.

(FEE IS FIXED OR
PER-UNIT?)(HOW DO WE MODEL ISP REVENUE? IMMEDIATE FUTURE)

The form of the auction mechanism presented here is (CAN BE? NEED TO SHOW TO
CLAIM 'IS') described as a \emph{locally}
pure-strategy progressive game with incomplete, but perfect information.
 you have perfect information, since you know what each move of the opponent is.
However, since you do not know the payoff function of the other player (which
will affect its behavior even if it does not alter your own victory conditions),
it is a game of incomplete information.
In the overall market analysis assumes complete, but perfect information.

 (WHAT
DOES NASH SAY ABOUT THIS?) (TRY MIXED? CAN ONLY HAVE MIXED WITH A DISTRIBUTED
VALUATION.. FUTURE WORK)

The paper is organized as follows...

(MOVED: TO ORGANIZE)\\
The main contribution of this work 
is an auction mechanism inspired by the classic PSP throughput problem. In
order to apply a distributed PSP implementation to the CMHK market,
we analize the behavior of users in a dynamical data exchange market. As both buyers and sellers are able
to change their bid strategies, and as each user only has \emph{local}
information about the bidding environment, it is clear that an unconstrained
market, even with a finite number of users, could suffer from the communication
expense from numerous local auctions trading an infinitely divisible resource.
We will assume that the cost of participating in the CMHK secondary market is
absorbed by the bid fee, which could represent data used in submitting bids, or
a fee charged per unit of data, or a flat rate charged at the completion of the
purchase. It is worth mentioning that CMHK users are not allowed to resell data
purchased from the CMHK
market, additionally, the purchased data does not carry to the next
service period. Therefore, a market equilibrium, where
supply equals demand, requires that users maintain incentive for truthfullness
across a distributed setting.
We complete a comprehensive analysis of market dynamics, (FINISH)
To the best of our knowledge, this is the first work to provide a truthful
mechanism in a distributed setting for data-exchange based on market behavior.
\\
\textbf{Remark:} It is certainly possible to extend the mechanism, alleviating the
restrictions introduced by the CMHK secondary market. We reserve this for
future work.

We claim that the CMHK market is
able to achieve an equilibrium as the sellers and buyers have an
incentive for a collaborative exchange, and as our mechanism provides
for effective communication between the connected users.

Despite the small message space, with many user types, there is no single
way to do the transformation from the direct revelation mechanism to the
desired one. Our mechanism is designed by guessing
right direct-revelation-to-desired-mechanism transformation and building it
into the allocation rule to be the primary step in the design. This incentive for a user to
truthfully reveal its type is built into the user strategies. As in classic
mechanism design, we determine the equilibria as result of incentive
compatibility in our mechanism design. 
We claim that in the CMHK market our formulation not only holds the desired VCG qualities,
but minimizes comminication overhead 
and auction duration, resulting in a convergence time (FIND COMPETITIVE RATIO?)
with respect to the classic throughput problem.

This is the (built-in) transformation from the
direct-revelation mechanism to the desired message space.

\subsection{Distributed Progressive Second Price Auctions}

@@

% MECHANISM
\subsubsection{The PSP Mechanism}\label{mechanism}
The PSP auction as given in \cite{lazar} and \cite{semret} is designed for the
problem of network bandwidth allocation, and is analyzed as a noncooperative
game where $i\in\mcI$ agents buy the
fixed amount of bandwidth $d_i^j$ from sellers $j\in\mcI$.
The market price function (MPF) for a buyer-seller pair is,
% NEW MARKET PRICE
\begin{align}\label{dataprice}
\begin{split}
    P_i^j(z, s_{-i})= \inf\bigg\lbrace y\ge 0 : D_i^j(y, s_{-i}) \ge z \bigg\rbrace,\\
\end{split}
\end{align}
and is the of minimum prices a user bids in
order to obtain bandwidth $z$ given opponent profile $s_{-i}$. 
The maximum available quantity of data in auction
$j$ at unit price $y$ given $s_{-i}^j$ is,
% NEW INVERSE DEMAND
\begin{align}\label{datapriceinverse}
\begin{split}
    D_i^j(y, s_{-i}) &= \bigg[ D^j - \sum_{p_k^j>y,k\ne i} d_k^j  \bigg]^+,
\end{split}
\end{align}
where $D^j$ is the total amount of bandwith that user $j$ has to offer.
% DATA ALLOCATION RULE
For each $i \in \mcI$, the allocation from auction $j$ is,
% and so for profile $s_i$, for any $i \in \mcI$,
\begin{align}\label{dataallocation}
    a_i^j(s) &= \min\bigg( d_i^j, 
    D_i^j(p_i^j,s_{-i}^j)\bigg).
\end{align}
Finally, we have the cost of the allocation,
% DATA COST
\begin{align}\label{datacost}
    c_i^j(s) = \displaystyle\sum_{k\ne i} 
p_k^j \big[a_k^j(0; s_{-i}^j)
    -a_k^j(s_i^j;s_{-i}^j)\big].
\end{align}

It was shown, in \cite{lazar}, that the mechanism may converge to a Nash market
equilibria for differentiated services
allocated between multiple agents when all players bid their real marginal valuation
of the bandwidth resource. In other words, the PSP constraints are
sufficient to attain the desirable property of truthfullness through incentive
compatibility. The pricing mechanism upholds the \emph{exclusion-compensation
principle}, user $i$
pays for its allocation so as to exactly cover the ``social opportunity cost"
which is given by the declared willingness to pay (bids) of the users who are
excluded by $i$'s presence, and thus also compensates the seller for the maximum lost potential
revenue \cite{lazar}.
The PSP rules assume that an agent's valuation is represented by an elastic valuation function.
\definition{\cite{lazar}}
A real valued function, $\theta(\cdot): [0,\infty) \rightarrow [0,\infty)$, is an \emph{(elastic) valuation
function} on $[0, D]$ if 
\begin{itemize}
    \item $\theta(0) = 0$,
    \item $\theta$ is differentiable,
    \item ${\theta}' \ge 0$, and ${\theta_i}'$ is non-increasing and continuous,
     \item There exists $\gamma > 0$, such that for all $z \in [0,D]$,
${\theta}'(z) > 0$ implies that for all $\eta \in [0, z), {\theta}'(z) \le
{\theta}'(\eta)
- \gamma(z - \eta)$. 
\end{itemize}
The function $\theta'(\cdot)$ on $[0, D]$ is called an (elastic) demand
function.
In the PSP market, a
user is considered truthful if their bid price equals their marginal valuation,
i.e. $p_i^j = {\theta_i^j}'$.

@@

We construct the model for a PSP data auction for mobile users
particpating in CMHK's secondary data-sharing market.
Define $\mcI = \lbrace 1, \cdots, I\rbrace$ as the set of users who purchase or sell
data from other users. We again define the bidding profile for any user to be 
$s \equiv
[s_i^j] \in \mcI \times \mcI$, and $s_{-i} \equiv [s_1^j , \cdots , s_{i-1}^j , s_{i+1}^j , \cdots
, s_I^j]_{j\in\mcI}$ as the profile of user $i$'s opponents. 
As a cellular network is fully connected, we assume that a buyer submits bids directly to sellers via the
cellular network. We assume that users are selfish, and therefore
rational. 
Users prefer to participate in the CMHK secondary market as it allows them to purchase
additional data for a cost less than the overage fee set by the ISP. 
Thus we assume that all users submit bids in order to maximize their
(private) valuation functions. 
In general, user preferences are defined by a utility function, $u$, which 
represents a users' valuation of an allocation minus the price.
Absent the cost or revenue from trading data, CMHK users gain utility from consuming
data. 
We assume that data is a unary resource belonging to the seller, and
therefore we identify each local auction with the identity of the seller
$j\in\mcI$.
We further show that user valuation satisfies the conditions for an
\emph{elastic demand function}, as in \cite{lazar}.
Finally, we assume in the CMHK market that a buyers' budget is always
sufficient, as the alternative is to pay the overage fee to the ISP.

@@

Consider the grid of bid proiles, $s$, representing the distributed PSP auction
mechanism in the CMHK market, each buyer $i$ will
have information from each seller $j$, as well as opponent profiles $s_{-i}$
from each auction in which it is participating, and therefore
in the extreme case, where $i$ submits bids to all auctions $j\in\mcI$, buyer
$i$ gains access to the full grid $s$. However, 
sellers can only gain information about the market grid by observing buyer
behavior in their local auction.
In our current formulation, we do not allow a seller to host multiple
auctions(FUTURE WORK?). Thus, the buyers are able to directly and globally
influence the CMHK market dynamics, with the sellers taking a secondary role
(FIND IN ANOTHER PAPER FOR SUPPORT OR OBVIOUS ENOUGH?).

@@

We assume that the CMHK market does not have network
bottlenecks, which is purely a bandwidth problem, as in \cite{semret}, and as
bandwidth in wireless networks is not the focus of this paper. We
conduct a comprehensive analysis, deriving a globally optimal strategy suited for
users with local information in a distrubuted data-sharing model.
